
\documentclass{beamer}
\usetheme{Madrid}
\usecolortheme{seahorse}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}

\title{La Gxoja Filozofio}
\subtitle{The Joy Philosophy}
\author{Anand Manikutty}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}{Overview}
\tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}{What is La Gxoja Filozofio?}
\begin{itemize}
    \item A new philosophy centered around joy, well-being, and human flourishing.
    \item Draws from Stoicism, Epicureanism, and Positive Psychology.
    \item Encourages intentional living through CHEATs: Comprehensive Happiness-Enhancing Activities and Tasks.
\end{itemize}
\end{frame}

\section{Origins and Inspiration}
\begin{frame}{Philosophical Lineage}
\begin{itemize}
    \item Inspired by ancient and modern philosophies.
    \item Like Stoicism, it emphasizes control over one’s inner state.
    \item Like Epicureanism, it values simple pleasures.
    \item Integrates empirical insights from modern happiness studies.
\end{itemize}
\end{frame}

\section{CHEATs}
\begin{frame}{What are CHEATs?}
\begin{itemize}
    \item CHEATs = Comprehensive Happiness-Enhancing Activities and Tasks.
    \item Daily, intentional actions backed by research in Positive Psychology.
    \item Examples: gratitude journaling, physical activity, acts of kindness, mindful reflection.
\end{itemize}
\end{frame}

\section{Core Tenets}
\begin{frame}{Five Core Principles}
\begin{enumerate}
    \item Joy is not a luxury; it is a goal.
    \item Reflection is as important as action.
    \item Habits shape identity and happiness.
    \item Happiness can be engineered.
    \item Community enhances meaning.
\end{enumerate}
\end{frame}

\section{Application}
\begin{frame}{Real-World Applications}
\begin{itemize}
    \item Personal life: Habit tracking, journaling, meaningful work.
    \item Workplaces: Mental wellness strategies, peer CHEAT groups.
    \item Education: Curriculum that includes emotional literacy and joy-based planning.
\end{itemize}
\end{frame}

\section{Comparison}
\begin{frame}{Comparison with Other Philosophies}
\begin{itemize}
    \item Less ascetic than Stoicism, more structured than Epicureanism.
    \item More actionable than Existentialism or Nihilism.
    \item Bridges traditional wisdom with modern science.
\end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
\begin{itemize}
    \item La Gxoja Filozofio offers a way to design a joyful life.
    \item Combines the best of ancient and modern thinking.
    \item We invite you to experiment with your own CHEATs.
\end{itemize}
\end{frame}

\begin{frame}{Thank You}
\centering
Questions? Thoughts? Let’s spread joy, one CHEAT at a time!

\bigskip
\href{https://github.com/qwykrtech}{github.com/qwykrtech}
\end{frame}

\end{document}
